Extending Graphical Representations for Compact Closed Categories with Applications to Symbolic Quantum Computation

### 2008-05-02 papers/reasoning-graphically/paper.tex
working on images...
git-svn-id: https://isaplanner.svn.sourceforge.net/svnroot/isaplanner/trunk/quantomatic@1470 f8f375fb-4f10-0410-8d47-b6fbdc7ca053

%\textbf{Matching.} 
To formalise the intuitive notion that a !-box
represents arbitrary number of copies of the subgraph made from its
nodes, we introduce \emph{!-box matching}. This is a binary relation
on graphs, written infix as $G \leq_! H$ when $G$ matches $H$. The set
matching !-box graphs is defined as the set closed by the following
operations on the !-boxes in a graph:

@@

%\textbf{Semantics.} 
We give a formal semantics to !-box graphs by defining them in terms
of a set of graphs in the underlying representation. We denote the
interpretation of a !-box graph $G$ by $\binterp{G}$ and say that
members of $\binterp{G}$ are instances of $G$.

>>>>

%\textbf{Matching.} 
To formalise the intuitive notion that a !-box represents arbitrary
number of copies of the subgraph made from its nodes, we introduce
\emph{!-box matching}. This is a binary relation on graphs, written
infix as $G \leq_! H$ when $G$ matches $H$. The set of !-box graphs
matching $G$ is defined as the set of graphs closed by the following
operations on $G$:

@@

\begin{figure}[t]
$$\begin{array}{ccccccc}
\inlinegraphic{3.8em}{bbox-ex1} & 
\frac{\leq}{copy} & \inlinegraphic{3.8em}{bbox-ex2}  & 
\frac{\leq}{merge} & \inlinegraphic{3.8em}{bbox-ex3}  & 
\frac{\leq}{drop} & \inlinegraphic{3.8em}{bbox-ex4}
\end{array}$$
\label{fig:bang-box-example}\caption{An illustration of !-box graph
  matching using the !-box operations. This involves first copying
  !-box $i_0$ twice, then merging $i_0$ and $i_1$ and finally dropping
  $i_3$.}
\end{figure}

%\textbf{Semantics.} 
An example of matching with these operations is illustrated in
Figure~\ref{fig:bang-box-example}.

We give a formal semantics to !-box graphs by defining them in terms
of a set of graphs in the underlying representation. We denote the
interpretation of a !-box graph $G$ by $\binterp{G}$ and say that
members of $\binterp{G}$ are instances of $G$.
